%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Nicola}{Moretto}
\position{Software Engineer}
\address{Italy}

\mobile{(+39) 333 4527335}
\email{n.moretto@nicolamoretto.eu}
% \homepage{nicolamoretto.eu}
\github{nicola88}
\linkedin{nmoretto}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
\skype{nicola.moretto88}
% \reddit{reddit-id}
\medium{n.moretto}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Canonical HR}
  {Canonical Group Limited\\5th Floor, Blue Fin Building\\110 Southwark Street\\SE1 0SU\\London, United Kingdom}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Engineer}
% How the letter is opened
\letteropening{Dear Sir or Madam}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Nicola Moretto~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

%Perché voglio lavorare con voi (motivazioni, esperienza, competenze)
%Perché voi dovreste prendere me / cosa ho da offrire

%\lettersection{Why Canonical?}
I graduated in Computer Science six years ago and since I enrolled in college Ubuntu has been at the foundation of my professional growth, helping me develop valuable skills and fostering my interest towards all aspects of an application development lifecycle. I consider this position an incredible opportunity to contribute to open-source technologies and products I - as many other people around the world - regularly use, love and are really passionate about.

%\lettersection{About Me}
I spent the last six years building back-end software systems for accounting firms, startups and established companies, using different technology stacks and software development methodologies, working with multidisciplinary and remote teams and improving work organization to satisfy software requirements and deadlines and deliver a clean, robust, reliable and well-documented product for clients or customers.

In 2014 I joined a startup willing to redesign their flagship product to meet growing demands in term of features and performance: an year later we delivered a brand new product based on a different technology stack, redesigned public and internal APIs and a complete rewrite of all semantic text analysis algorithms to run on a distributed computing environment, a project I was the main developer and maintainer.

In 2017 a small remote team looking for a back-end developer asked me to review and test their PHP web application four months ahead of public release. In that time frame we successfully completed all tests, fixed several critical issues and carried out significant updates to improve application performance, security and maintainability.

In 2018 I built a Python web application providing NLU capabilities for a suite of chatbot applications, currently running hundred of thousands conversations each day.

%\lettersection{Why Me?}
Let me know if you are interested in my profile.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
